Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-28 ECCV/paper.tex
Cropped output files, removed space between figures and text
Cleaned up bibliography, added table related to blur angle range

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}

@@

\section{Related Work}
Our problem may be classified broadly in two areas; fiducial markers and
tracking. So, we will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure} 
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  Pi-Tag\cite{Pitag13}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{newconcentric_01.pdf}  
  Our Fiducial  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

@@

@@

\section{Experimental Validation}
First, we have used synthetic images to test resilience to blur. We have scaled
down ARTag fiducial and our fiducial to size 150x150.  Then, we blurred both
fiducials along all orientations using different scales. Finally, we tried to
detect ARTag in these blurred images using ALVAR library\cite{alvar} and our fiducial
using algorithm given in previous section.

%\begin{tabular}

%\end{tabular}
Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
\setlength{\floatsep}{5pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
\setlength{\intextsep}{5pt plus 2pt minus 2pt}

@@

\section{Related Work}
Our problem may be classified broadly in two areas; fiducial markers and
tracking. So, we will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure} 
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  Pi-Tag\cite{Pitag13}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}  
  Our Fiducial  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

@@

We conducted a small experiment to test ARTag's resilience towards blur.
We scaled down ARTag fiducial to size 150x150.  Then, we blurred ARTag 
at various orientations using different scales. Finally, we tried to detect
ARTag in these blurred images using ALVAR library\cite{alvar}.

\begin{table}
\caption{Recognition rate of AR Tag at various blur scales}
\centering
\begin{tabularx}{0.75\textwidth}{c *{6}{|Y}|}
\cline{2-6}
& \multicolumn{5}{ c |}{Recognition Rate (in percent)} \\
\cline{2-6} & \multicolumn{5}{ c |}{Blur Scale} \\ \cline{2-6}
& 30 & 35 & 40 & 45 & 50 \\ \cline{1-6}
\multicolumn{1}{ | c | }{ARTAg} & 100 & 19 & 9 & 5 & 0 \\ \cline{1-6}
\cline{1-6}
\end{tabularx}
\label{tab:ARTag_blur}
\end{table}

From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
ARTag drastically with increase in blur scale.

We have also analysed the recognition rate along different blur orientations at
different blur scales. We found that per blur scale, at certain blur
orientations, recognition of ARTag fails. Table shows the range of blur angles
for which we are able to recognise the ARTag at different blur scales.

\begin{table}
\caption{Blur angle range}
\centering
\begin{tabularx}{0.75\textwidth}{|Y|Y|}
\cline{1-2}
Blur Scale & Blur Angle Range \\ \cline{1-2}
35 & 32--58 \\ \cline{1-2}
40 & 41--48 \\ \cline{1-2}
45 & 41--48 \\ \cline{1-2}
50 & 44--46 \\ \cline{1-2}
\end{tabularx}
\end{table}

@@

\section{Experimental Validation}

Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.
